The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
L473
L468

Note that $\Gamma_1$ depends on $e_\text{b}$, and so it is only a constant in the case of a test particle. For $j>0$, we must compute the precession timescale ourselves. The time coordinate used in Section \ref{sec:rk} is $\tau \equiv \alpha' t$. $\alpha'$ is defined by \citet[see eq. 3.9]{farago2010}, and we write it as
\begin{equation}
    \alpha' \equiv \frac{3}{4} \Omega_\text{b} \left(\frac{a_\text{b}}{r}\right)^{7/2} f(1-f) \,\Gamma_2(j,f,a_\text{b}/r, e_\text{b}) \, ,
\end{equation}
where we have written the $\sqrt{1+m_\text{r}/M_\text{b}}$ factor as $\Gamma_2$. Written in terms of our variables, this expression is very complicated, and we choose to compute it numerically for simplicity. Note, however, that except for extremely large $j$ (e.g. $>10$), $\Gamma_2 \sim 1$.

Given some precession timescale in code units $\tau_\text{p}$, we can calculate the precession timescale
\begin{equation}
    \label{eq:tp-j}
    t_\text{p} = \frac{4}{3}\Omega_\text{b}^{-1} \left(\frac{r}{a_\text{b}}\right)^{7/2} \frac{\tau_\text{p}}{f(1-f)\Gamma_2}\, .
\end{equation}
Compared to the precession timescale for a test particle, that is
\begin{equation}
    \label{eq:tp-rat}
    \frac{t_{\text{p,}j}}{t_{\text{p,}j=0}} = \frac{\tau_\text{p}}{4\,\Gamma_1\,\Gamma_2} \, .
\end{equation}

@@

>>>>

Note that $\Gamma_1$ depends on $e_\text{b}$, and so it is only a constant in the case of a test particle. For $j>0$, we must compute the precession timescale ourselves. The time coordinate used in Section \ref{sec:rk} is $\tau \equiv \alpha' t$. $\alpha'$ is defined by \citet[see eq. 3.9]{farago2010}, and we write it as
\begin{equation}
    \alpha' \equiv \frac{3}{4} \Omega_\text{b} \left(\frac{a_\text{b}}{r}\right)^{7/2} f(1-f) \,\Gamma_2(j,f,a_\text{b}/r, e_\text{b}) \, ,
\end{equation}
where we have written the $\sqrt{1+m_\text{r}/M_\text{b}}$ factor as $\Gamma_2$. \RR{$m_\text{r}$ is the mass of the ring. To compute $\Gamma_2$ from our variables requires finding the roots of a cubic equation (see equation (\ref{eq:gamma2-eq})). However, for low $j$ (e.g. $<10$), $m_\text{r} \ll M_\text{b}$ and $\Gamma_2 \sim 1$.}

Given \RR{$\tau_\text{p}$, the precession timescale in code units, we can calculate the precession timescale in physical units}
\begin{equation}
    \label{eq:tp-j}
    t_\text{p} = \frac{4}{3}\Omega_\text{b}^{-1} \left(\frac{r}{a_\text{b}}\right)^{7/2} \frac{\tau_\text{p}}{f(1-f)\Gamma_2}\, .
\end{equation}
Compared to the precession timescale for a test particle, that is
\begin{equation}
    \label{eq:tp-rat}
    \frac{t_{\text{p,}j}}{t_{\text{p,}j=0}} = \frac{\tau_\text{p}}{4\,\Gamma_1\,\Gamma_2} \, .
\end{equation}

@@

\appendix

\section{Computing $\Gamma_2$}
\RR{
Equation (3.9) from \citet{farago2010} includes a term $\sqrt{1 + m_\text{r}/M_\text{b}}$ where $m_\text{r}$ is the mass of the ring and $M_\text{b}$ is the mass of the binary host. To find the value of this expression in our own variables is non-trivial. Here we define
\begin{equation}
    \Gamma_2 = \sqrt{1 + \frac{m_\text{r}}{M_\text{b}}}\, .
\end{equation}
}

\RR{
We can write
\begin{equation}
    \label{eq:gamma2-eq}
    \Gamma_2^3 - \Gamma_2 - j\,f\,(1-f)\,\sqrt{\frac{a_\text{b}}{r}\,(1-e_\text{b}^2)} = 0\, ,
\end{equation}
and solve for $\Gamma_2$ using the Newton-Raphson method.
}

### 2025-04-04 src/tex/review.tex
L468

>>>>

    \begin{response}
        {L468: Again, I think m\_r was not defined earlier. I assume this is the mass of the ring. Also, would it be possible to write down the expression of Gamma\_2 to effectively see that it tends to 1 when j is large? Since it is very complicated it could go in the Appendix to avoid interrupting the flow of the section.}
        We have added text to define $m_\text{r}$. We also added a section in the appendix to describe the process of computing $\Gamma_2$. However, we also clarified in the text why $\Gamma_2$ tends to 1 for small $j$, so this section may no longer be necessary.
    \end{response}
